Affective Uplift During Video Game Play: A Naturalistic Case Study

### 2024-04-04 ms.Rmd
Uncompress if not yet

# Download, unzip data from OSF PWS database
PWS_DATA_PATH <- Sys.getenv("PWS_DATA_PATH", unset = "data-raw/data.zip")
if (!file.exists(PWS_DATA_PATH)) {
  dir.create(
    dirname(PWS_DATA_PATH), 
    showWarnings = FALSE, 
    recursive = TRUE
  )
  download.file(
    url = "https://osf.io/download/j48qf/",
    destfile = PWS_DATA_PATH
  )
  dir.create("data", FALSE)
  unzip(
    zipfile = PWS_DATA_PATH,
    files = c(
      "data/demographics.csv",
      "data/study_prompt_answered.csv"
    )
  )
}

>>>>

# Download data from OSF PWS database
PWS_DATA_PATH <- Sys.getenv("PWS_DATA_PATH", unset = "data-raw/data.zip")
if (!file.exists(PWS_DATA_PATH)) {
  dir.create(
    dirname(PWS_DATA_PATH), 
    showWarnings = FALSE, 
    recursive = TRUE
  )
  download.file(
    url = "https://osf.io/download/j48qf/",
    destfile = PWS_DATA_PATH
  )
}

# unzip required data tables
if (!file.exists("data/demographics.csv")) {
  dir.create("data", FALSE)
  unzip(
    zipfile = PWS_DATA_PATH,
    files = c(
      "data/demographics.csv",
      "data/study_prompt_answered.csv"
    )
  )
}
